Reproducible Workflow on a Public Cloud for Computational Fluid Dynamics

### 2019-04-09 tex/MesnardoBarba2019.tex
Read over manuscript (see list)
* Force coefficients figure: use black lines for 2D data and show up to 80 time units.
* Use capitalized titles for sub-sections.
* GPU available late 2016, IB support for NC-series available during 2017.
* Add missing words or correct wrong usage.
* Re-phrase some sentences in Results section.
* Add small explanation about RMDA.
* Re-write paragraph on reproducibility packages.
* (WIP) Mention Zenodo repository that contains output data needed to reproduce figures.
* Add NSF grant in "Acknowledgments" section.

\subsection{Use of container technology}

@@

\subsection{Use of public cloud resources}

@@

The top concerns of researchers considering cloud computing are performance and cost. 
Until just a few years ago, the products offered by cloud providers were unsuitable to the needs of computational scientists using HPC, due to performance overhead of virtualization and lack of support for fast networking. 
Azure only introduced nodes with GPU devices and Infiniband support in 2017. 
Our first objective was to assess performance on cloud nodes for the type of computations in our research workflows with  tightly coupled parallel applications. 
We present results from benchmarks and test-cases showing that we are able to obtain similar performance in terms of latency and bandwidth using the Azure virtual network, comparing to a traditional university-managed HPC cluster (Colonial One).
Table \ref{tab:hw_specs} lists the hardware specifications of the nodes used on Microsoft Azure and Colonial One.
 Our target research application relies on three-dimensional CFD simulations with our in-house research software. We include here a sample of the types of results needed to answer our research question, obtained by running on the public cloud using the reproducible workflow described in Section \ref{sec:workflow}. 
 The goal is to showcase the potential of cloud computing for CFD, share the lessons we learned in the process, as well as analyze the cost scenarios for full applications.

@@

Point-to-point MPI benchmarks from the Ohio State University Micro-Benchmarks\footnote{OSU Micro-Benchmarks (version 5.6): \url{http://mvapich.cse.ohio-state.edu/benchmarks/}} suite ran on Microsoft Azure and Colonial One to investigate performance in terms the latency and bandwidth.
The latency test is carried out in a ping-pong fashion and measures the time elapsed to get a response; the sender sends a message with a certain data size and wait for the receiver to send back the message with the same data size.
The bandwidth test measures the maximum sustained rate that can be achieved on the network; it consists in having the sender sends a fixed number of messages to a receiver that replies only after receiving all of them.
The tests ran on \texttt{NC24r} nodes on Azure and \texttt{Ivygpu} nodes on Colonial One, all them featuring a network interface for RDMA (Remote Direct Memory Access) connectivity to communicate over an InfiniBand network.
Fig. \ref{fig:osu_benchmarks} reports the mean latencies and bandwidths obtained over $5$ repetitions on both platforms.

@@

CFD algorithms often require to solve linear systems with iterative methods.
For example, the project method implemented in our research software solve a Poisson system every time step to project the velocity field onto the divergence-free space (to satisfy the incompressibility constraint).
Thus, we investigated the time-to-solution to solve a three-dimensional Poisson system (obtained with a 7-point stencil using central differences) on different nodes of Microsoft Azure and Colonial One.
The system was solved using a Conjugate-Gradient (CG) method with a classical Algebraic MultiGrid (AMG) preconditioner with an exit criterion set to an absolute tolerance of $10^{-12}$.
The iterative solver ran on CPU nodes (\texttt{H16r} instances on Azure and \texttt{Short} nodes on Colonial One) using the CG algorithm from the PETSc library\cite{balay_et_al_2018} and an AMG preconditioner from Hypre BoomerAMG.
Fig. \ref{fig:poisson_benchmarks} (top) reports the mean runtimes (averaged over $5$ repetitions) to iteratively solve the system, on a uniform grid of $50$ million cells ($1000 \times 1000 \times 50$), as we increase the number of nodes in the pool.
We also solved the Poisson system with the NVIDIA AmgX library on multiple GPU devices using \texttt{NC24r} instances on Azure and \texttt{Ivygpu} nodes on Colonial One.
The Poisson system for a base mesh of $6.25$ million cells ($500 \times 500 \times 25$) is solved on a single node using $12$ MPI processes and $2$ GPU devices; we then double the mesh size as we double the number of nodes.
As the number of iterations to reach convergence increases with the size of the system, we normalize the runtimes by the number of iterations.
Fig. \ref{fig:poisson_benchmarks} (bottom left) shows the normalized mean runtimes ($5$ repetitions) obtained on Azure and Colonial One.
The bottom-right panel of the figure reports the normalized mean runtimes obtained on Azure when we put more constraint on the bandwidth; the base mesh now contains $25$ millions cells ($1000 \times 500 \times 50$).

@@

Our research lab is interested in understanding the aerodynamics of flying animals using Computational Fluid Dynamics software.
One of our applications deals with the aerodynamics of a snake species, \textit{Chrysopelea Paradisi}, that lives in South-East Asia.
The arboreal reptile has the remarkable capacity to turn its entire body into a wing and glide over several meters\cite{socha_2011}.
The so-called flying snake jumps from tree branches, undulates in the air, and is able to produce lift by expanding its ribcage to flatten its ventral surface (morphing its normally circular cross-section into a triangular shape).

To study the flow around the flying snake, we develop a in-house CFD software called PetIBM\cite{chuang_et_al_2018}, a open-source toolbox that solves the two- and three-dimensional incompressible Navier-Stokes equations using a projection method (an approximate block-LU decomposition of the fully discretized equations\cite{perot_1993}) and an Immersed-Boundary Method (IBM).
Within this framework, the fluid equations are solved on a extended grid that does not conform to the surface of the immersed body.
To model the presence of the body, the momentum equation is augmented with a forcing term that is activated in the vicinity of the immersed boundary.
This technique allows the use of simple fixed structured Cartesian grids to solve the equations.
PetIBM also implements Immersed Boundary Methods (IBMs) that fit into the projection method and, in the present study, we use an implementation of the IBM proposed in \cite{li_et_al_2016}.
PetIBM runs on distributed-memory architectures and relies on the efficient data structures and parallel routines of the PETSc library.
The software also implements the possibility to solve linear systems on multiple GPU devices distributed across the nodes with the NVIDIA AmgX and AmgXWrapper\cite{chuang_barba_2017}.
To obtain reproducible computational results, the code used to run the simulations needs to be made available.
In that regard, PetIBM is open source, version-controlled on GitHub,\footnote{PetIBM (version 0.4): \url{https://github.com/barbagroup/PetIBM}} and developed under the permissive BSD-3 clause license.

@@

With Batch Shipyard, we submitted a job on Azure Batch to compute the two-dimensional flow around an anatomically accurate sectional shape of the gliding snake.
The cross-section has a chord-length of $1$ and forms a $35$-degree angle of attack with the incoming freestream flow.
The Reynolds number, based on the freestream speed, the body chord-length, the kinematic viscosity, is set to $Re=2000$.
The immersed boundary is centered in a $30c \times 30c$ computational domain that contains just above $2.9$ million cells.
The grid is kept uniform with the highest resolution in the vicinity of the body and stretched to the external boundaries with a constant ratio (see Table \ref{tab:grid_specs} for details about the grid).
(The immersed boundary is discretized with the same resolution than the background fluid grid.)
A convective condition was used at the outlet boundary while freestream conditions were enforced on the others.
The job was submitted to a pool of two \texttt{NC24r} nodes, with $12$ MPI processes and $2$ GPU devices per node.
The task completed $200,000$ time steps (i.e., $80$ time units of flow simulation with a time-step size $\Delta t = 0.0004 c / U_\infty$) in just above $7$ hours.

@@

Although the two-dimensional simulations gave us some insights into to flow dynamics happening in the behind the snake, we know that at this Reynolds number ($Re = 2000$), three-dimensional will develop in the wake.
Thus, we submitted jobs to Azure Batch to perform direct numerical simulation of the three-dimensional flow around a cylinder with the same anatomically accurate cross-section.
The computational domain is extended in the $z$-direction over a length of $3.2c$ and the grid now contains about $46$ million cells (uniform discretization in the $z$-direction; see Table \ref{tab:grid_specs}).
The grid is kept uniform in the $z$-direction and we enforce periodic conditions at the front and back boundaries.
The simulation ran in a Docker container on Azure Batch using Batch Shipyard.
The job was submitted to a pool of two \texttt{NC24r} nodes using $24$ MPI processes and $4$ GPU devices per node.
The task completed $100,000$ time steps ($100$ time units with a time-step size $\Delta t = 0.01 c / U_\infty$) in about $5$ days and $16$ hours.

@@

Fig. \ref{fig:wz_avg_3d} shows the instantaneous spanwise vorticity averaged along the $z$-direction after $80$ and $100$ time units.
Compared to the snapshots from the two-dimensional simulation, we observe that (1) free-shear layers roll up into vortices further away from the snake body and (2) the von Karman street exhibits a narrower wake.
We note the presence of an unsteady recirculation region just behind the snake cylinder and alternating regions of positive and negative cross-flow velocity showing the presence of von Karman vortices (Fig. \ref{fig:ux_uy_xz_plane_3d}).
Fig. \ref{fig:qcrit_wx_3d} shows the isosurfaces of the Q-criterion after $100$ time units and highlights the complexity of the three-dimensional turbulent wake generated by the snake model.

@@

\begin{table*}[!h]
    \renewcommand{\arraystretch}{1.5}
    \caption{Details about the computational grids used for the snake simulations with PetIBM.}
    \label{tab:grid_specs}
    \centering
        \begin{tabular}{clllll}
        Case & Domain & Uniform region & Smallest cell-width & Stretching ratio & Size \\
        \hline
        2D & $30 \times 30$ & $\left[ -0.52, 3.48 \right] \times \left[ -2, 2 \right]$ & $0.004 \times 0.004$ & $1.01$ & $1704 \times 1706$ \\
        3D & $30c \times 30c \times 3.2c$ & $\left[ -0.52, 3.48 \right] \times \left[ -2, 2 \right] \times \left[ 0, 3.2 \right]$ & $0.008 \times 0.008 \times 0.08$ & $1.01$ & $1071 \times 1072 \times 40$ \\
        \hline
    \end{tabular}
\end{table*}

@@

For the year $2018$, Microsoft Azure granted our research lab a sponsorship in terms of cloud credits to run CFD simulations with our in-house software.
We a ``pay-as-you-go'' type of subscription, users can directly sees how much it costs to run a scientific application on a public cloud; such information is often hidden to end-users on university-managed clusters.
From May to December, we spend a total of $20,614$ USD to run simulations of the gliding snake.
During that period, we have been charged data management, networking, storage, bandwidth, and virtual machines (Table \ref{tab:azure_charges}).
More than $99\%$ of the charges are due the usage of virtual machines.
We had the opportunity to use different instances on Microsoft Azure and most the charges for the usage of virtual machines of the \texttt{NC24r} instance (used for the two- and three-dimensional simulations of the flying snake).
The \texttt{NC24r} instance is part of the NC-series (Table \ref{tab:nc_series}); we copiously used as it enables RDMA capabilities for our MPI application and features NVIDIA K80 GPU devices.
For example, the two-dimensional snake run reported in the present article cost $55.4$ USD ($2$ \texttt{NC24r} instances with a hourly price of $3.96$ USD for about $7$ hours).
The three-dimensional computation cost $1077.1$ USD ($2$ \texttt{NC24r} instances for about $136$ hours).

@@

Command-line tools such as Azure-CLI and Batch Shipyard were greatly helpful to create and submit everything from our local terminal. (In our research lab, we tend to avoid, as much as possible, interacting with graphical-user interfaces, so as to make our workflow more reproducible.)
Azure-CLI helped us to setup the Azure Batch account and its associated Azure Storage, as well as uploading/downloading our simulation data.
With Batch Shipyard, users do not need to have experience with the Azure Batch SDK.
We have used Batch Shipyard to submit jobs on Azure Batch to run Docker container-based multi-tasks.
Note that Batch Shipyard also support Singularity containers.

@@

In a new effort to make our research transparent and reproducible by others, we have version-controlled all the input files, pre- and post-processing scripts, as well as the Dockerfiles (used to create the Docker images), the Batch Shipyard configuration files, and command-line instructions required to rerun the simulations on Microsoft Azure.
In addition, all the scripts to reproduce the figures in the present article are made available.
The reproducibility packages are hosted on GitHub in the repository \texttt{cloud-repro}.\footnote{\url{https://github.com/barbagroup/cloud-repro}}

 \section*{Acknowledgment}

This study was possible thanks to a sponsorship from the Microsoft Azure for Research program,\footnote{Microsoft Azure for Research: \url{https://www.microsoft.com/en-us/research/academic-program/microsoft-azure-for-research/}}.

>>>>

\subsection{Use of Container Technology}

@@

\subsection{Use of Public Cloud Resources}

@@

The top concerns of researchers considering cloud computing are performance and cost. 
Until just a few years ago, the products offered by cloud providers were unsuitable to the needs of computational scientists using HPC, due to performance overhead of virtualization and lack of support for fast networking. 
Azure only introduced nodes with GPU devices during late 2016 and Infiniband support for the NC-series in 2017.
Our first objective was to assess performance on cloud nodes for the type of computations in our research workflows with  tightly coupled parallel applications. 
We present results from benchmarks and test-cases showing that we are able to obtain similar performance in terms of latency and bandwidth using the Azure virtual network, comparing to a traditional university-managed HPC cluster (Colonial One).
Table \ref{tab:hw_specs} lists the hardware specifications of the nodes used on Microsoft Azure and Colonial One.
Our target research application relies on three-dimensional CFD simulations with our in-house research software. We include here a sample of the types of results needed to answer our research question, obtained by running on the public cloud using the reproducible workflow described in Section \ref{sec:workflow}.
The goal is to showcase the potential of cloud computing for CFD, share the lessons we learned in the process, as well as analyze the cost scenarios for full applications.

@@

Point-to-point MPI benchmarks from the Ohio State University Micro-Benchmarks\footnote{OSU Micro-Benchmarks (version 5.6): \url{http://mvapich.cse.ohio-state.edu/benchmarks/}} suite ran on Microsoft Azure and Colonial One to investigate performance in terms the latency and bandwidth.
The latency test is carried out in a ping-pong fashion and measures the time elapsed to get a response; the sender sends a message with a certain data size and wait for the receiver to send back the message with the same data size.
The bandwidth test measures the maximum sustained rate that can be achieved on the network; it consists in having the sender sends a fixed number of messages to a receiver that replies only after receiving all of them.
The tests ran on \texttt{NC24r} nodes on Azure and \texttt{Ivygpu} nodes on Colonial One, all of them featuring a network interface for RDMA (Remote Direct Memory Access) connectivity to communicate over an InfiniBand network.
(RDMA allows direct access to a remote's memory without involving the operating system of the host and remote.)
Fig. \ref{fig:osu_benchmarks} reports the mean latencies and bandwidths obtained over $5$ repetitions on both platforms.

@@

CFD algorithms often require to solve linear systems with iterative methods.
For example, the projection method implemented in our software solve a Poisson system every time step to project the velocity field onto the divergence-free space (to satisfy the incompressibility constraint).
Thus, we investigated the time-to-solution to solve a three-dimensional Poisson system (obtained with a 7-point stencil central-difference scheme) on different nodes of Microsoft Azure and Colonial One.
The system was solved using a Conjugate-Gradient (CG) method with a classical Algebraic Multi-Grid (AMG) preconditioner with an exit criterion set to an absolute tolerance of $10^{-12}$.
The iterative solver ran on CPU nodes (\texttt{H16r} instances on Azure and \texttt{Short} nodes on Colonial One) using the CG algorithm from the PETSc library\cite{balay_et_al_2018} and an AMG preconditioner from Hypre BoomerAMG.
Fig. \ref{fig:poisson_benchmarks} (top) reports the mean runtimes (averaged over $5$ repetitions) to iteratively solve the system, on a uniform grid of $50$ million cells ($1000 \times 1000 \times 50$), as we increase the number of nodes in the pool.
We also solved the Poisson system with the NVIDIA AmgX library on multiple GPU devices using \texttt{NC24r} instances on Azure and \texttt{Ivygpu} nodes on Colonial One.
The Poisson system for a base mesh of $6.25$ million cells ($500 \times 500 \times 25$) is solved on a single node using $12$ MPI processes and $2$ GPU devices; we then double the mesh size as we double the number of nodes.
As the number of iterations to reach convergence increases with the size of the system, we normalize the runtimes by the number of iterations.
Fig. \ref{fig:poisson_benchmarks} (bottom left) shows the normalized mean runtimes ($5$ repetitions) obtained on Azure and Colonial One.
The bottom-right panel of the figure reports the normalized mean runtimes obtained on Azure when we put more constraint on the bandwidth; the base mesh now contains $25$ millions cells ($1000 \times 500 \times 50$).

@@

Our research lab is interested in understanding the aerodynamics of flying animals via CFD simulations.
One of our applications deals with the aerodynamics of a snake species, \textit{Chrysopelea Paradisi}, that lives in South-East Asia.
The arboreal reptile has the remarkable capacity to turn its entire body into a wing and glide over several meters\cite{socha_2011}.
The so-called ``flying snake'' jumps from tree branches, undulates in the air, and is able to produce lift by expanding its ribcage to flatten its ventral surface (morphing its normally circular cross-section into a triangular shape).

To study the flow around the flying snake, we develop a in-house CFD software called PetIBM\cite{chuang_et_al_2018}, a open-source toolbox that solves the two- and three-dimensional incompressible Navier-Stokes equations using a projection method (seen as an approximate block-LU decomposition of the fully discretized equations\cite{perot_1993}) and an Immersed-Boundary Method (IBM).
Within this framework, the fluid equations are solved over a extended grid that does not conform to the surface of the immersed body.
To model the presence of the body, the momentum equation is augmented with a forcing term that is activated in the vicinity of the immersed boundary.
This technique allows the use of simple fixed structured Cartesian grids to solve the equations.
PetIBM also implements Immersed Boundary Methods (IBMs) that fit into the projection method and, in the present study, we use an implementation of the IBM proposed in \cite{li_et_al_2016}.
PetIBM runs on distributed-memory architectures using the efficient data structures and parallel routines from the PETSc library.
The software also implements the possibility to solve linear systems on multiple GPU devices distributed across the nodes with the NVIDIA AmgX and AmgXWrapper\cite{chuang_barba_2017}.
One of the requirements to produce reproducible computational results is the make the code available.
In that regard, PetIBM is open source, version-controlled on GitHub,\footnote{PetIBM (version 0.4): \url{https://github.com/barbagroup/PetIBM}} and developed under the permissive BSD-3 clause license.

@@

With Batch Shipyard, we submitted a job on Azure Batch to compute the two-dimensional flow around an anatomically accurate sectional shape of the gliding snake.
The cross-section has a chord-length of $1$ and forms a $35$-degree angle of attack with the incoming freestream flow.
The Reynolds number, based on the freestream speed, the body chord-length, the kinematic viscosity, is set to $Re=2000$.
The immersed boundary is centered in a $30c \times 30c$ computational domain that contains just above $2.9$ million cells.
The grid is kept uniform with the highest resolution in the vicinity of the body and stretched to the external boundaries with a constant ratio (see Table \ref{tab:grid_specs} for details about the grid).
(The immersed boundary is discretized with the same resolution than the background fluid grid.)
A convective condition was used at the outlet boundary while freestream conditions were enforced on the three other boundaries.
The job was submitted to a pool of two \texttt{NC24r} nodes, using $12$ MPI processes and $2$ GPU devices per node.
The task completed $200,000$ time steps (i.e., $80$ time units of flow simulation with time-step size $\Delta t = 0.0004 c / U_\infty$) in just above $7$ hours.

@@

Although the two-dimensional simulations gave us some insights into to flow dynamics happening in the behind the snake, we know that at this Reynolds number ($Re = 2000$), three-dimensional structures will develop in the wake.
Thus, we submitted jobs to Azure Batch to perform direct numerical simulation of the three-dimensional flow around snake model: a cylinder with the same anatomically accurate cross-section.
The computational domain is extended in the $z$-direction over a length of $3.2c$ and the grid now contains about $46$ million cells (with a uniform discretization in the $z$-direction; see Table \ref{tab:grid_specs}).
The grid is kept uniform in the $z$-direction and we enforce periodic conditions at the front and back boundaries.
The simulation ran in a Docker container on Azure Batch using Batch Shipyard.
The job was submitted to a pool of two \texttt{NC24r} nodes using $24$ MPI processes and $4$ GPU devices per node.
The task completed $100,000$ time steps ($100$ time units with a time-step size $\Delta t = 0.01 c / U_\infty$) in about $5$ days and $16$ hours.

@@

Fig. \ref{fig:wz_avg_3d} shows the instantaneous spanwise vorticity averaged along the $z$-direction after $80$ and $100$ time units.
Compared to the snapshots from the two-dimensional simulation, we observe that (1) free-shear layers roll up into vortices further away from the snake body and (2) the von Karman street exhibits a narrower wake.
We also note the presence of an unsteady recirculation region just behind the snake cylinder and alternating regions of positive and negative cross-flow velocity showing the presence of von Karman vortices (Fig. \ref{fig:ux_uy_xz_plane_3d}).
Fig. \ref{fig:qcrit_wx_3d} shows a side-view of the isosurfaces of the Q-criterion after $100$ time units and highlights the complexity of the three-dimensional turbulent wake generated by the snake model.

@@

\begin{table*}[!h]
    \renewcommand{\arraystretch}{1.5}
    \caption{Details about the computational grids used for the snake simulations with PetIBM. Distances are expressed in terms of chord-length units.}
    \label{tab:grid_specs}
    \centering
        \begin{tabular}{clllll}
        Case & Domain & Uniform region & Smallest cell-width & Stretching ratio & Size \\
        \hline
        2D & $30 \times 30$ & $\left[ -0.52, 3.48 \right] \times \left[ -2, 2 \right]$ & $0.004 \times 0.004$ & $1.01$ & $1704 \times 1706$ \\
        3D & $30 \times 30 \times 3.2$ & $\left[ -0.52, 3.48 \right] \times \left[ -2, 2 \right] \times \left[ 0, 3.2 \right]$ & $0.008 \times 0.008 \times 0.08$ & $1.01$ & $1071 \times 1072 \times 40$ \\
        \hline
    \end{tabular}
\end{table*}

@@

For the year $2018$, Microsoft Azure granted our research lab a sponsorship in terms of cloud credits to run CFD simulations with our in-house software.
With a ``pay-as-you-go'' subscription, users can immediately sees how much it costs to run a scientific application on a public cloud; such information is often hidden to end-users on university-managed clusters.
From May to December, we spend a total of $20,614$ USD to run simulations of the gliding snake.
During that period, we have been charged for data management, networking, storage, bandwidth, and virtual machines (Table \ref{tab:azure_charges}).
More than $99\%$ of the charges incurred were for the usage of virtual machines, mainly instances from the NC-series (Table \ref{tab:nc_series}).
To run PetIBM simulations of the snake model, we used the \texttt{NC24r} virtual machines to get access to NVIDIA K80 GPUs and InfiniBand networking.
For example, the two-dimensional snake run reported in the present article cost $55.4$ USD ($2$ \texttt{NC24r} instances with a hourly price of $3.96$ USD for about $7$ hours).
The three-dimensional computation cost $1077.1$ USD ($2$ \texttt{NC24r} instances for about $136$ hours).

@@

Command-line tools such as Azure-CLI and Batch Shipyard were greatly helpful to create and submit everything from our local terminal. (In our research lab, we tend to avoid, as much as possible, interacting with graphical-user interfaces, to make our workflow more reproducible.)
Azure-CLI helped us to setup the Azure Batch account and its associated Azure Storage, as well as uploading/downloading simulation data.
With Batch Shipyard, we did not need to have experience with the software development kit to use Azure Batch.
We have used Batch Shipyard to submit jobs on Azure Batch to run Docker container-based multi-instance tasks.
Note that Batch Shipyard also support Singularity containers.

@@

In a new effort to make our research transparent and reproducible by others, we have version-controlled all the files necessary to re-run the examples highlighted in this paper.
The repository \texttt{cloud-repro}\footnote{\url{https://github.com/barbagroup/cloud-repro}} is hosted on GitHub.
The reproducibility packages contains input files, Batch Shipyard configuration files, command-line instructions to setup and submit jobs to Microsoft Azure, as well as the post-processing scripts to reproduce the figures of this paper.
Although they are not required to reproduce the computations, the Dockerfiles to build Docker images are also made available.
These files contain details about the all libraries installed to create the computational runtime environment.
In addition, we have also uploaded to Zenodo all output data required to just reproduce the figures of the present paper.

\section*{Acknowledgments}

This study was possible thanks to a sponsorship from the Microsoft Azure for Research program\footnote{Microsoft Azure for Research: \url{https://www.microsoft.com/en-us/research/academic-program/microsoft-azure-for-research/}} and supported by NSF Grant No. CCF-1747669.
